Diamonds data set exploration
========================================================
***
# Problem set 1

### Task 1 "Diamonds"
```{r}
# Load ggplot2 and diamonds data set 
library(ggplot2)
data(diamonds)

# Checking variables and main parameters
summary(diamonds)
names(diamonds)
```

### Task 2 "Price Histogram"
```{r}
# Histogram of the price of all the diamonds in the diamond data set.
ggplot(data = diamonds, aes(x = price)) + 
	geom_histogram()
```

### Task 3 "Price Histogram Summary"
* Noticeable spike in the diamonds' price range from 625 to 1 250; 
* Median price is 2 410;
* Mean price is 3 932.8;
* Distribution is close to normal.

### Task 4 "Diamond Counts"
```{r}
#how many diamonds cost less than 500$?
nrow(subset(diamonds, price < 500))

#how many diamonds cost less than 250$?
nrow(subset(diamonds, price < 250))

#how many diamonds cost 15 000$ or more?
nrow(subset(diamonds, price >= 15000))

```

### Task 5 "Cheaper Diamonds"
```{r}
#some manipulations with x axis
ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(color = "white", fill = "darkblue", binwidth = 500) +
  scale_x_continuous(limits = c(0, 20000), breaks = seq(0, 20000, 2500)) + 
  xlab("Price of the diamonds") + 
  ylab("Quantity of the diamonds")

#looks like two patterns of normal distribution
ggplot(data = diamonds, aes(x = log10(price))) +
  geom_histogram(color = "white", fill = "darkblue", binwidth = 0.05) + 
  xlab("Price of the diamonds") + 
  ylab("Quantity of the diamonds")

```

### Task 6 "Price by Cut Histogram"
```{r}
library(gridExtra)
levels(diamonds$cut)

pbc1 <- ggplot(data = subset(diamonds, cut == "Fair"), aes(x = price)) +
          geom_histogram(color = "white", fill = "darkblue")  

pbc2 <- ggplot(data = subset(diamonds, cut == "Good"), aes(x = price)) +
          geom_histogram(color = "white", fill = "darkblue")

pbc3 <- ggplot(data = subset(diamonds, cut == "Very Good"), aes(x = price)) +
          geom_histogram(color = "white", fill = "darkblue")

pbc4 <- ggplot(data = subset(diamonds, cut == "Premium"), aes(x = price)) +
          geom_histogram(color = "white", fill = "darkblue")

pbc5 <- ggplot(data = subset(diamonds, cut == "Ideal"), aes(x = price)) +
          geom_histogram(color = "white", fill = "darkblue")

grid.arrange(pbc1, pbc2, pbc3, pbc4, pbc5, ncol = 3)

#more direct approach
qplot(x = price, data=diamonds, binwidth = 500) +
  geom_histogram() +
  facet_wrap(~cut, ncol=2, scales="free_y")
```

### Task 7 "Price by Cut"
```{r}
#Which cut has the highest priced diamond?
by(diamonds$price, diamonds$cut, max)

#Which cut has the lowest priced diamond?
by(diamonds$price, diamonds$cut, min)

#Which cut has the lowest median price?
by(diamonds$price, diamonds$cut, median)

```

### Task 8 "Scales and Multiple Histograms"
```{r}
qplot(x = price, data=diamonds, binwidth = 500) +
  geom_histogram() +
  facet_wrap(~cut, ncol=2, scales="free_y")
```

### Task 9 "Price per Carat by Cut"
```{r}
qplot(x = price/carat, data=diamonds) +
  geom_histogram() +
  facet_wrap(~cut, ncol=2, scales="free_y") +
  scale_x_log10()
```

### Task 10 "Price box plots"
```{r}
#Clarity by price
uniform <- subset(diamonds, (color == "D" | color =="E")  & carat < 1 & carat > 0.8)
uniform2 <- subset(diamonds, (color == "F" | color =="G")  & carat < 2.2 & carat > 1.8)
uniform3 <- subset(diamonds, (color == "H" | color =="I" | color == "J") &   carat < 3.5 & carat > 2)
p1 <- qplot(x=clarity, y=price, data = uniform, geom ='boxplot')
p2 <- qplot(x=clarity, y=price, data = uniform2, geom ='boxplot')
p3 <- qplot(x=clarity, y=price, data = uniform3, geom ='boxplot')
grid.arrange(p1,p2, p3, ncol =1)

#Color by price
qplot(x = color, y = price, data = diamonds,
      binwidth = 50,
       geom = 'boxplot',
       xlab = 'Diamond color',
       fill = color) +
     scale_y_continuous( breaks = seq(0,8000,500)) +
     coord_cartesian(ylim = c(0,8000))

#Price by cut
qplot(x=cut, y=price, data=diamonds, geom="boxplot", fill=cut) +
  coord_cartesian(ylim=c(0, 10000)) +
  theme(legend.position="None")

```

### Task 11 "Interquartile Range (IQR)"
```{r}
by(diamonds$price, diamonds$color, summary)
by(diamonds$price, diamonds$color, IQR)
```

### Task 12 "Price per Carats Box and Plots by Color"
```{r}
qplot(data=diamonds, x=color, y=price/carat) +
  geom_boxplot(fill="darkgrey") +
  coord_cartesian(ylim=c(2000,6000)) +
  xlab('Color of diamonds') + ylab('Price/Carat relation of the diamonds') +
  ggtitle('Middle 50% of the price distributions from the best to the worst colors of diamonds')

uniform <- subset(diamonds,cut == "Ideal" & clarity == "IF" & carat < 1.2 & carat > 0.8)
qplot(data=uniform, x=color, y=price/carat) +
  geom_boxplot(fill="darkgrey")

```

### Task 13 "Carat frequency polygon"
```{r}
table(diamonds$carat)[table(diamonds$carat)>2000]
```


***
# Problem set 2

### Task 1 "Price vs X"
```{r}
data(diamonds)
names(diamonds)
ggplot(data = diamonds, aes(x = price, y = x)) +
  geom_point()

```

### Task 2 "Correlations"
```{r}
cor.test(diamonds$price, diamonds$x)
cor.test(diamonds$price, diamonds$y)
cor.test(diamonds$price, diamonds$z)
```

### Task 3 "Price vs Depth"
```{r}
ggplot(data = diamonds, aes(x = depth, y = price)) +
  geom_point()

```

### Task 4 "Adjustments - Price vs Depth"
```{r}
ggplot(data = diamonds, aes(x = depth, y = price)) +
  geom_point(alpha = 1/100) +
  scale_x_continuous(breaks = seq(0, 80, 2))

```

### Task 5 "Typical Depth Range"
```{r}
by(diamonds$price, diamonds$depth, summary)
```

### Task 6 "Correlation - Price and Depth"
```{r}
cor.test(diamonds$price, diamonds$depth)

```

### Task 7 "Price vs Carat"
```{r}
ggplot(data = diamonds, aes(x = price, y = carat)) + 
  geom_point() + 
  xlim(0, quantile(diamonds$price, 0.99)) +
  ylim(0, quantile(diamonds$carat, 0.99))
```

### Task 8 "Price vs Volume"
```{r}
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
ggplot(data = diamonds, aes(x = price, y = volume)) + 
  geom_point()

```

### Task 9 "Correlation on subsets"
```{r}
diamonds.volume_filtered <- subset(diamonds, diamonds$volume > 0 & diamonds$volume <= 800)
cor.test(diamonds.volume_filtered$price, diamonds.volume_filtered$volume)

```

### Task 10 "Adjustments - Price vs Volume"
```{r}
ggplot(diamonds.volume_filtered, aes(x = price, y = volume)) + 
  geom_point(alpha = 1 / 20) +
  geom_smooth(method = "lm")
```

### Task 11 "Mean price by clarity"
```{r}
install.packages("dplyr")
library(dplyr)

diamondsByClarity <- diamonds %.%
  group_by(clarity) %.%
  summarise(mean_price = mean(price),
            median_price = median(price),
            min_price = min(price),
            max_price = max(price),            
            n = n()) %.%
  arrange(clarity)
  
head(diamondsByClarity)
```

### Task 12 "Bar Charts of Mean Price"
```{r}
library(dplyr)
library(gridExtra)

diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))

head(diamonds_by_clarity)

p1 <- ggplot(data = diamonds_by_clarity, aes(x = clarity)) +
        geom_bar()

p2 <- ggplot(data = diamonds_by_color, aes(x = color)) +
        geom_bar()

grid.arrange(p1, p2, ncol = 1)


p3 <- ggplot(data = diamonds_mp_by_clarity, aes(x = clarity)) +
        geom_bar()

p4 <- ggplot(data = diamonds_mp_by_color, aes(x = color)) +
        geom_bar()

grid.arrange(p3, p4, ncol = 1)

```

***
# Problem set 3

### Task 1 "Price histogram with facet and color"
```{r}
library(ggplot2)
data(diamonds)
head(diamonds)

ggplot(data = diamonds, aes(x = price)) +
  geom_histogram(aes(fill = cut)) +
  scale_x_log10() +
  facet_wrap(~color)
```

### Task 2 "Price vs table color by cut"
```{r}
ggplot(data = diamonds, aes(x = table, y = price)) +
  geom_point(aes(color = cut)) +
  scale_color_brewer(type = "qual") + 
  coord_cartesian(xlim = c(50, 80)) +
  scale_x_continuous(breaks = seq(50, 80, 2))
```

### Task 3 "Price vs volume and diamond clarity"
```{r}
diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
head(diamonds)

ggplot(data = diamonds, aes(x = volume, y = price)) +
  geom_point(aes(color = clarity)) +
  scale_y_log10() + 
  xlim(0, quantile(diamonds$volume, 0.99)) +
  scale_color_brewer(type = 'div')
```

### Task 4 "Price carat bind"
```{r}
ggplot(data = diamonds, aes(x = cut, y = price/carat)) +
  geom_jitter(aes(color = color)) +
  facet_wrap(~clarity) +
  scale_color_brewer(type = 'div')
```

***
# Diamonds & Price Predictions

### Scatterplot review
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
	scale_x_continuous(lim = c(0, quantile(diamonds$carat, 0.99))) +
	scale_y_continuous(lim = c(0, quantile(diamonds$price, 0.99))) +
	geom_point(fill = I("#F79420"), color = I("black"), shape = 21)
```

### ggPairs Function
```{r}
# install these if necessary
install.packages('GGally')
install.packages('scales')
install.packages('memisc')
install.packages('lattice')
install.packages('MASS')
install.packages('car')
install.packages('reshape')
install.packages('plyr')

# load the ggplot graphics package and the others
library(ggplot2)
library(GGally)
library(scales)
library(memisc)

# sample 10,000 diamonds from the data set
set.seed(20022012)
diamond_samp <- diamonds[sample(1:length(diamonds$price), 10000), ]
ggpairs(diamond_samp, params = c(shape = I('.'), outlier.shape = I('.')))
```

### The Demand of Diamonds
```{r}
library(gridExtra)

plot1 <- qplot(diamonds, price, binwidth = 100, fill = I("#099DD9")) + 
  ggtitle('Price') +
  geom_histogram()

plot2 <- qplot(diamonds, price, binwidth = 0.01, fill = I("#F79420")) +
  ggtitle('Price (log10)') +
  geom_histogram() + 
  scale_x_log10()

grid.arrange(plot1, plot2, ncol = 1)
```

### Scatterplot transformation
```{r}
# Create a new function to transform the carat variable
cuberoot_trans = function() trans_new('cuberoot', transform = function(x) x^(1/3),
                                      inverse = function(x) x^3)

# Use the cuberoot_trans function
ggplot(aes(carat, price), data = diamonds) + 
  geom_point() + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

### Overplotting revisited
```{r}
ggplot(aes(carat, price), data = diamonds) + 
  geom_point(alpha = 1/2, size = 3/4, position = "jitter") + 
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat')
```

### Price vs Carat by Clarity
```{r}
library(RColorBrewer)

ggplot(aes(x = carat, y = price), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
    guide = guide_legend(title = 'Clarity', reverse = T,
    override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
    breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
    breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity') + 
  scale_color_brewer()
```

### Price vs Carat by Cut
```{r}
ggplot(aes(x = carat, y = price, color = cut), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Cut', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Clarity')
```

### Price vs Carat by Color
```{r}
ggplot(aes(x = carat, y = price, color = Color), data = diamonds) + 
  geom_point(alpha = 0.5, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Color', reverse = T,
                                          override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous(trans = cuberoot_trans(), limits = c(0.2, 3),
                     breaks = c(0.2, 0.5, 1, 2, 3)) + 
  scale_y_continuous(trans = log10_trans(), limits = c(350, 15000),
                     breaks = c(350, 1000, 5000, 10000, 15000)) +
  ggtitle('Price (log10) by Cube-Root of Carat and Color’)
```
