Diamonds data set exploration
========================================================
***
# Problem set 1

### Task 1 "Diamonds"
```{r}
# Load ggplot2 and diamonds data set 
library(ggplot2)
data(diamonds)

# Checking variables and main parameters
summary(diamonds)
names(diamonds)
```

### Task 2 "Price Histogram"
```{r}
# Histogram of the price of all the diamonds in the diamond data set.
ggplot(data = diamonds, aes(x = price)) + 
	geom_histogram()
```

### Task 3 "Price Histogram Summary"
* Noticeable spike in the diamonds' price range from 625 to 1 250; 
* Median price is 2 410;
* Mean price is 3 932.8;
* Distribution is close to normal.

### Task 4 "Diamond Counts"
```{r}
#how many diamonds cost less than 500$?
nrow(subset(diamonds, price < 500))

#how many diamonds cost less than 250$?
nrow(subset(diamonds, price < 250))

#how many diamonds cost 15 000$ or more?
nrow(subset(diamonds, price >= 15000))

```

### Task 5 "Cheaper Diamonds"
```{r}

```

### Task 6 "Price by Cut Histogram"
```{r}

```

### Task 7 "Price by Cut"
```{r}

```

### Task 8 "Scales and Multiple Histograms"
```{r}

```

### Task 9 "Price per Carat by Cut"
```{r}

```

### Task 10 "Price box plots"
```{r}

```

### Task 11 "Interquartile Range (IQR)"
```{r}

```

### Task 12 "Price per Carats Box and Plots by Color"
```{r}

```

### Task 13 "Carat frequency polygon"
```{r}

```

### Task 14 "Gapminder Data"
```{r}

```

### Task 15 "Exploring your Friends' Birthday"
```{r}

```

***
