Several variables
========================================================
### Third Qualitative Variable
```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_histogram()
```


### Plotting Conditional Summaries
```{r Plotting Conditional Summaries}

```


### Reshaping Data
```{r}
install.packages('reshape2')
library(reshape2)
```


### Ratio Plot
```{r Ratio Plot}

```


### Third Quantitative Variable
```{r Third Quantitative Variable}

```


### Cut a Variable
```{r Cut a Variable}

```


### Plotting it All Together
```{r Plotting it All Together}

```


### Plot the Grand Mean
```{r Plot the Grand Mean}

```


### Friending Rate
```{r Friending Rate}

```


### Friendships Initiated

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}

```


### Bias-Variance Tradeoff Revisited
```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```


### Histograms Revisited
```{r Histograms Revisited}

```


### Number of Purchases
```{r Number of Purchases}

```


### Prices over Time
```{r Prices over Time}

```


### Looking at Samples of Households
```{r Looking at Sample of Households}

```


### Heat Maps
```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```
