Several variables
========================================================
### Third Qualitative Variable
```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_histogram()
       
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() +
  stat_summary(fun.y = mean, geom = "point", shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) + 
  geom_line(aes(color = gender), stat = "summary", fun.y = median)

library(dplyr)
pf.fc_by_age_gender <- pf %.%
  filter(!is.na(gender)) %.%
  group_by(age, gender) %.%
  summarise(mean_friend_count = mean(friend_count),
    median_friend_count = median(friend_count),
    n = n()) %.%
  ungroup() %.%
  arrange(age)
```


### Plotting Conditional Summaries
```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = friend_count), 
            data = subset(pf.1, !is.na(gender))) +   
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```


### Reshaping Data
```{r}
install.packages('reshape2')
library(reshape2)
library(dplyr)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
  age ~ gender,
  value.var = "median_friend_count")

head(pf.fc_by_age_gender.wide)

pf.fc_by_age_gender.wide <- pf.fc_by_age_gender %.% 
  group_by(age) %.% 
  summarise(male = friend_count.median[gender = 'male'], 
                      female = friend_count.median[gender = 'female'], 
                      ratio = female / male) %.% 
  arrange(age)

head(pf.fc_by_age_gender.wide)
```


### Ratio Plot
```{r Ratio Plot}
# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash

ggplot(aes(x = age, y = female / male),
        data = pf.fc_by_age_gender.wide) + 
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)
```


### Third Quantitative Variable
```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - pf$tenure/365)
```


### Cut a Variable
```{r Cut a Variable}
summary(pf.year_joined)
table(pf.year_joined)

pf$year_joined.bucket <- cut(pf.year_joined,
  c(2004, 2009, 2011, 2012, 2014))
```


### Plotting it All Together
```{r Plotting it All Together}
table(pf$year_joined.bucket, useNA = "ifany")

ggplot(aes(x = age, y = friend_count),
  data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = "summary", fun.y = median)
```


### Plot the Grand Mean
```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count),
  data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), 
    stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = mean, linetype = 2)
```


### Friending Rate
```{r Friending Rate}
with(subset(pf, tenure >= 1), summary(friend_count / tenure))
```


### Friendships Initiated
```{r Friendships Initiated}
ggplot(aes(x = tenure, y =friendships_initiated / tenure),
    data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket))
```


### Bias-Variance Tradeoff Revisited
```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
    data = subset(pf, tenure >= 1)) +
  geom_smooth(aes(color = year_joined.bucket))
```


### Histograms Revisited
```{r Histograms Revisited}
yo <- read.csv("yogurt.csv")
str(yo)
yo$id <- factor(yo$id)
str(yo)
qplot(data = yo, x = price, fill = I("#F79420"))
```


### Number of Purchases
```{r Number of Purchases}

```


### Prices over Time
```{r Prices over Time}

```


### Looking at Samples of Households
```{r Looking at Sample of Households}

```


### Heat Maps
```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```
