Lesson 3
========================================================
### Pseudo-Facebook User Data
```{r Pseudo-Facebook User Data}
getwd()
list.files()
pf <- read.csv('pseudo_facebook.tsv', sep = "\t")
```


### Histogram of Users' Birthdays
```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```


### Faceting
```{r Faceting}
qplot(data = pf, x = dob_day) +
  scale_x_discrete(breaks=1:31)
```


#### What code would you enter to create a histogram of friend counts?
```{r Friend Count}
qplot(data = pf, x = friend_count,
      xlim = c(0, 1000))
ggplot(data = pf, aes(x = friend_count)) +
  geom_histogram(colour = "white", binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

```


### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```


### Omitting NA Values and Statistics 'by' Gender
```{r Statistics \'by\' Gender}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```


### Tenure
```{r Tenure}
qplot(data = pf, x = tenure, 
      color = I("black"), fill=I("#099dd9"))
```


#### How would you create a histogram of tenure by year?
```{r Tenure Histogram by Year}
qplot(data = pf, x = tenure/365, binwidth = 0.5,
      color = I("black"), fill=I("#099dd9"))

ggplot(aes(x = tenure/365), data = pf) + 
  geom_histogram(binwidth = .25, color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) + 
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```


### The Spread of Memes and Add a Scaling Layer
```{r Add a Scaling Layer}
install.packages("gridExtra")
library(gridExtra)

p1 <- qplot(x = friend_count, data = pf)
p2 <- qplot(x = log10(friend_count+1), data = pf)
p3 <- qplot(x = sqrt(friend_count), data = pf)
grid.arrange(p1, p2, p3, ncol = 1)
```


### Frequency Polygons
```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')
```


### Likes on the Web
```{r Likes on the Web}
by(pf$www_likes, pf$gender, sum)
```


### Box Plots, Quartiles, and Friendships
```{r Box Plots, Quartiles, and Friendships}
# box plot: scale limit removes data from calculation
qplot(x = gender, y = friend_count,
	data = subset(pf, !is.na(gender)),
	geom = "boxplot") +
	scale_x_continuous(limits = c(0, 1000))

# box plot: coord_cartesian zoom in or zoom out plot without changing data
qplot(x = gender, y = friend_count,
	data = subset(pf, !is.na(gender)),
	geom = "boxplot") +
	coord_cartesian(ylim = c(0, 250))

# friend requests
qplot(x = gender, y = friendships_initiated,
	data = subset(pf, !is.na(gender)),
	geom = "boxplot")

by(pf$friendships_initiated, pf$gender, summary)
```


#### Write about some ways that you can verify your answer.
```{r Friend Requests by Gender}

```


### Getting Logical
```{r Getting Logical}

```
