Lesson 4
========================================================
### Scatterplots
```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = "\t")
qplot(data = pf, x = age, y = friend_count)
```


### ggplot Syntax
```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() +
  xlim(13, 90)
```


### Overplotting
```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(Alpha = 1/20) +
  xlim(13, 90)
```


### Coord_trans()
```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(Alpha = 1/20 position = position_jitter(h = 0)) +
  xlim(13, 90) +
  Coord_trans(y = "sqrt")
```


### Alpha and Jitter
```{r Alpha and Jitter}

```


### Conditional Means
```{r Conditional Means}

```

Create your plot!

```{r Conditional Means Plot}

```


### Overlaying Summaries with Raw Data
```{r Overlaying Summaries with Raw Data}

```


### Correlation
```{r Correlation}

```


### Correlation on Subsets
```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```


### Create Scatterplots
```{r}

```


### Strong Correlations
```{r Strong Correlations}

```


```{r Correlation Calcuation}
#What's the correlation betwen the two variables? Include the top 5% of values 
#for the variable in the calculation and round to 3 decimal places.

```


### More Caution with Correlation
```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```


### Noisy Scatterplots
```{r Noisy Scatterplots}

```

### Making Sense of Data
```{r Making Sense of Data}

```


### Understanding Noise: Age to Age Months
```{r Understanding Noise: Age to Age Months}

```


### Age with Months Means
```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```


### Noise in Conditional Means
```{r Noise in Conditional Means}

```


### Smoothing Conditional Means
```{r Smoothing Conditional Means}

```
