Tools for two variables exploration
========================================================
### Scatterplots
```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = "\t")
qplot(data = pf, x = age, y = friend_count)
```


### ggplot Syntax
```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() +
  xlim(13, 90)
```


### Overplotting
```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(Alpha = 1/20) +
  xlim(13, 90)
```


### Coord_trans()
```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(Alpha = 1/20 position = position_jitter(h = 0)) +
  xlim(13, 90) +
  Coord_trans(y = "sqrt")
```


### Alpha and Jitter
```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data(pf)) + 
	geom_jitter(Alpha = 1/10,  position = position_jitter(h = 0))
	Coord_trans(y = "sqrt")
```


### Conditional Means
```{r Conditional Means}
install("dplyr")
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summaries(age_groups,
					friend_count_mean = mean(friend_count),
					friend_count_median = median(friend_count),
					n = n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)

#Introduction to dplyr
#http://rstudio-pubs-static.s3.amazonaws.com/11068_8bc42d6df61341b2bed45e9a9a3bf9f4.html
pf %.%
	group_by(age) %.%
	summaries(friend_count_mean = mean(friend_count),
				friend_count_median = median(friend_count),
				n = n()) %.%
	arrange(age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = friend_count, y = age), data = pf.fc_by_age) +
	geom_line()
```


### Overlaying Summaries with Raw Data
```{r Overlaying Summaries with Raw Data}
ggplot(aes(age, friend_count), data = pf) +
	xlim(13, 90) +
	geom_point(Alpha = 0.005,
				position = position_jitter(h = 0),
				color = 'orange') +
	Coord_trans(y = "sqrt") + 
	geom_line(stat = "summary", fun.y = mean) +
	geom_line(stat = "summary", fun.y = quantile, probs = 0.1,
				linetype = 2, color = "blue") +
	geom_line(stat = "summary", fun.y = quantile, probs = 0.9,
				linetype = 2, color = "blue")
```


### Correlation
```{r Correlation}
cor.test(pf$age, pf$friend_count, method = "pearson")
cor.test(pf$age, pf$friend_count, method = "student")
with(pf, cor.test(age, friend_count, method = "pearson"))
```


### Correlation on Subsets
```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```


### Create Scatterplots
```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + 
	geom_point()
```


### Strong Correlations
```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) + 
	geom_point() +
	xlim(0, quantile(pf$www_likes_received, 0.95)) +
	ylim(0, quantile(pf$likes_received, 0.95))
	geom_smooth(method = "lm", color = "red")
```


```{r Correlation Calcuation}
#What's the correlation betwen the two variables? Include the top 5% of values 
#for the variable in the calculation and round to 3 decimal places.
cor.test(pf$www_likes_received, pf$likes_received)
```


### More Caution with Correlation
```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
?Mitchell
```

Create your plot!

```{r Temp vs Month}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
	geom_point()
```


### Noisy Scatterplots
```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)
```

### Making Sense of Data
```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
	geom_point() +
	scale_x_discrete(breaks = seq(0, 203, 12))
```


### Understanding Noise: Age to Age Months
```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +
	geom_line()

head(pf.fc_by_age, 10)
pf.fc_by_age[17:19, ]

pf$age_with_months <- pf$age + (1 - pf$dob_month / 12)
pf$age_with_months <- with(pf, age + (1 - dob_month / 12))
```


### Age with Months Means
```{r Age with Months Means}
library(dplyr)
pf.fc_by_age_months <- pf %.%
	group_by(age_with_months) %.%
	summarise(friend_count_mean = mean(friend_count),
		friend_count_median = median(friend_count),
		n = n()) %.%
	arrange(age_with_months)

head(pf.fc_by_age_months)
```


### Noise in Conditional Means
```{r Noise in Conditional Means}
ggplot(aes(x = age_with_months, y = friend_count_mean),
		data = subset(pf.fc_by_age_months, age_with_months < 71)) +
		geom_line()
```


### Smoothing Conditional Means
```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x = age_with_months, y = friend_count_mean),
		data = subset(pf.fc_by_age, age < 71)) +
		geom_line() + 
		geom_smooth()

p2 <- ggplot(aes(x = age_with_months, y = friend_count_mean),
		data = subset(pf.fc_by_age_months, age_with_months < 71)) +
		geom_line() + 
		geom_smooth()

p2 <- ggplot(aes(x = round(age / 5) * 5, y = friend_count),
		data = subset(pf, age_ < 71)) +
		geom_line(stat = "summary", fun.y = mean) 

library(gridExtra)
grid.arrange(p2, p1, p3, ncol = 1)
```

